SDSS-IV MaNGA: The Radial Profile of Enhanced Star Formation in Close Galaxy Pairs

### 2020-10-20 maintex.tex
updated authors list

\author{
Joshua~L.~Steffen\altaffilmark{1}, Hai~Fu\altaffilmark{1}, J.~M.~Comerford\altaffilmark{2}, Shuai~Feng\altaffilmark{3}, Cheng~Li\altaffilmark{4}, Y.~Sophia~Dai\altaffilmark{5}, and Rui~Xue\altaffilmark{1}
}
\altaffiltext{1}{Department of Physics \& Astronomy, University of Iowa, Iowa City, IA 52242}
\altaffiltext{2}{Department of Astrophysical and Planetary Sciences, University of Colorado, Boulder, CO 80309}
\altaffiltext{3}{Key Laboratory for Research in Galaxies and Cosmology, Shanghai Astronomical University, Chinese Academy of Sciences}
\altaffiltext{4}{Tsinghua Center for Astrophysics and Physics Department, Tsinghua University, Beijing 100084, China}
\altaffiltext{5}{Chinese Academy of Sciences South America Center for Astronomy (CASSACA), 20A Datun Road, Beijing 100012, China}

>>>>

\include{authors}
